---
title: "Positive Covid-19 Test Percentages by State"
date: "6/3/2020"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/macka/Documents/covid-resources/code")

library(psych)
library(usmap)
library(tidyverse)

```

## Loading Covid Tracking Data 

State cumulative testing data called from [Covid Tracking](https://covidtracking.com).  

```{r load.packages.data, include = F}

CT.url <- "https://covidtracking.com/api/v1/states/current.csv"

states.current <- read_csv(url(CT.url))

states.current <- select(states.current, state, fips, positive, totalTestResults)

# Load 2019 state population data from census

POP.url <- "https://raw.githubusercontent.com/mackaytc/covid-resources/master/data/state-pop-census-2019.csv"

pop <- read_csv(url(POP.url)) 

pop$fips <- fips(pop$NAME)

data <- inner_join(states.current, pop, by = "fips") 

data <- rename(data, 
               state.name = NAME, 
               positive.tests = positive, 
               pop.2019 = POPESTIMATE2019, 
               total.test.results = totalTestResults) %>% 
  select(state.name, fips, pop.2019, positive.tests, total.test.results)

rm(CT.url, states.current, POP.url, pop)

```

## Current Positive Test Percentages

Per [Covid Tracking](https://covidtracking.com/api), we have the following variable definitions: 

 * `positive`: total cumulative positive test results in a given state
 * `totalTestResults`: calculated value (positive + negative) of total test results
 
Code below calculates the cumulative positive percentage of total tests by state (``pct.positive``) and the number of tests per capita (``tests.per.capita``) and prints table sorted in ascending order of tests per capita. Data is also saved in ``.csv`` for easier [viewing online](https://github.com/mackaytc/covid-resources/blob/master/code/tests-pct-positive.csv). 


```{r calc.pct.positive}

# Subset data + calculate pct.positive = pos. tests / total tests

data <- data %>% mutate(pct.positive = (positive.tests / total.test.results)*100, 
                        pct.positive = round(pct.positive, 1), 
                        tests.per.capita = total.test.results / pop.2019, 
                        tests.per.capita = round(tests.per.capita, 4)) %>% 
  arrange(tests.per.capita)

# Summary stats for both new measures

describe(data$pct.positive)
describe(data$tests.per.capita)

# Table sorted in descending value of positive percentage

print(data)

# Save .csv version of table 

write_csv(data, "tests-pct-positive.csv")

```

